---
title: "SMU_DDS_6306-403_HW#4"
author: "Jack K. Rasmus-Vorrath"
date: "June 4, 2017"
output: html_document
---

# Question 1a

### Log of a Positive Number
```{r Question 1a}
log(5)

```

# Question 1b

### The default base of log() is e

#### Different bases can be used with different functions or different inputs to the 'base' argument
```{r Question 1b}
log(5, base = exp(1))

log(5, base = 2)

log2(5)

```

# Question 1c

### Logs of negative numbers do not exist
```{r Question 1c}
log(-1)
```

# Question 1d

### Square roots can be taken with the sqrt() function
```{r Question 1d}
sqrt(4)
```

# Question 2a

### Vector of 15 standard normal random values, whose mean and standard deviation are calculated after generation
```{r Question 2a}
x <- rnorm(15)

x

mean(x)

sd(x)
```

# Question 2b

### Vector of 15 standard normal random values of mean 10 and standard deviation 2, whose mean and standard deviation are again calculated after generation
```{r Question 2b}
y <- rnorm(15, 10, 2)

y

mean(y)

sd(y)
```

# Question 2c

### NB (above): Measures calculated after random number generation will not precisely match argument inputs, and depend on the particular randomization seed


# Question 3a

### Weights of 6 individuals in KG
```{r Question 3a}
weights <- c(60, 72, 57, 90, 95, 72)
```

# Question 3b

### Heights of 6 individuals in M
```{r Question 3b}
heights <- c(1.80, 1.85, 1.72, 1.90, 1.74, 1.91)
```

# Question 3c

### Weight and Height vector output
```{r Question 3c}
weights

heights
```

# Question 3d

### Simple scatterplot of Weight v. Height, indicating a general positive correlation, with one high leverage point at (95, 1.74)
```{r Question 3d}
plot(weights, heights, main = "Scatterplot of Weight v. Height: 6 Individuals", xlab = "Weight", ylab = "Height", pch = 19)
```

# Question 3e

### BMI for 6 individuals: Weight / Height^2
```{r Question 3e}
BMI <- weights/(heights)^2

BMI
```

# Question 3f

### Mean Weight calculation
```{r Question 3f}
mean(weights)
```

# Question 3g

### Calculated deviation from the mean
```{r Question 3g}
meanDifference <- weights - mean(weights)

meanDifference
```

# Question 3h

### Sum of deviation from the mean (non-squared!)
```{r Question 3h}
sum(meanDifference)
```

# Question 4

### Jack's Data Science profile
```{r Question 4}
Jack <- data.frame(Skills = c("Computer Programming", "Math", "Statistics", "Machine Learning", "Domain Expertise", "Communication & Presentation Skills", "Data Visualization"), Ranking = c(3, 5, 4, 3, 5, 5, 2))

library(ggplot2)

levels(Jack$Skills) <- gsub(" ", "\n", levels(Jack$Skills))

ggplot(Jack, aes(Skills, Ranking)) + geom_col()
```





















